Paper 1 Notebook

### 2023-11-08 minos/outcomes/paper_1_notebook.Rmd
part one of updating paper plots]

raw_model_formula_string <- "SF_12 ~ factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state_raw) + 
                  relevel(factor(job_sec), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_netinc)"
raw_model_formula <- as.formula(raw_model_formula_string)
variables <- all.vars(raw_model_formula)
variables[1] <- "SF_12"

@@

model_formula_string <- "SF_12 ~ factor(sex) +  relevel(factor(ethnicity), ref='WBI') + scale(age) + factor(education_state) + factor(S7_labour_state) + relevel(factor(job_sec), ref=1) + relevel(factor(region), ref='London') + scale(hh_income)"

@@

```{r ols_handovers}
start.data <- crossval.raw.data[which(crossval.raw.data$time==2013),]
handover.data <- start.data
for (i in 1:7){
  start.data$SF_12 <- predict(sf12.lm, start.data)
  start.data[, 'time'] <- start.data[, 'time'] +1
  handover.data <- rbind(handover.data, start.data[, c("pidp", "SF_12", "time")])
}

>>>>

raw_model_formula_string <- "SF_12 ~ factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state_raw) + 
                  relevel(factor(job_sec), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_netinc) + factor(loneliness)"
raw_model_formula <- as.formula(raw_model_formula_string)
variables <- all.vars(raw_model_formula)
variables[1] <- "SF_12"

@@

model_formula_string <- "SF_12 ~ factor(sex) +  relevel(factor(ethnicity), ref='WBI') + scale(age) + factor(education_state) + factor(S7_labour_state) + relevel(factor(job_sec), ref=1) + relevel(factor(region), ref='London') + scale(hh_income) + factor(housing_quality) + factor(loneliness) + factor(neighbourhood_safety)"

@@

```{r ols_handovers}
start.data <- crossval.raw.data[which(crossval.raw.data$time==2013),]
handover.data <- start.data[, c("pidp", "SF_12", "time")]
for (i in 1:7){
  start.data$SF_12 <- predict(sf12.lm, start.data)
  start.data[, 'time'] <- start.data[, 'time'] +1
  handover.data <- rbind(handover.data, start.data[, c("pidp", "SF_12", "time")])
}
